Dual selection games

### 2018-09-27 articles/dual-selection-games/article.tex
prepare dual game paper for arxiv

The duality of the Rothberger game \(\schStrongSelGame{\mc O_X}{\mc O_X}\)
and the point-open game on \(X\) for perfect information strategies
was first noted by Galvin in \cite{MR0493925}, and
for Markov-information strategies by Clontz and Holshouser in
[TODO cite]. These proofs may be generalized as follows.

@@

In the case that \(\mc B=\mc O_X\), \(\schStrongSelGame{\mc O_X}{\mc O_X}\) is the well-known Rothberger game,
and \(\schStrongSelGame{\mc P_X}{\neg\mc O_X}\) is isomorphic
to the point-open game \(PO(X)\): \(\plI\) chooses points of \(X\), \(\plII\) chooses an open neighborhood
of each chosen point, and \(\plI\) wins if \(\plII\)'s choices are a cover.
So this was simply the classic result that the Rothberger game and
point-open game are perfect-information dual \cite{MR0493925}, and the more recent result that
these games are Markov-information dual [TODO cite clontzHols].

@@

Note that in the case that \(\mc B=\Omega_X\), \(\schStrongSelGame{\Omega_X}{\Omega_X}\) is the Rothberger
game played with \(\omega\)-covers, and \(\schStrongSelGame{\mc F_X}{\neg\Omega_X}\) is isomorphic
to the \(\Omega\)-finite-open game \(\Omega FO(X)\): \(\plI\) chooses finite subsets of \(X\), \(\plII\) chooses an open neighborhood
of each chosen finite set, and \(\plI\) wins if \(\plII\)'s choices are an \(\omega\)-cover.
These games were shown to be dual in [TODO cite clontzHols].

@@

In the case that \(\mc B=\Omega_{X,x}\) for some \(x\in X\), \(\schStrongSelGame{\mc D_X}{\Omega_{X,x}}\) is
the strong countable dense fan-tightness game at \(x\), see e.g. \cite{MR2678950}. \(\schStrongSelGame{\mc T_X}{\neg\Omega_{X,x}}\)
is the game \(CL(X,x)\) first studied by Tkachuk in \cite{tkachukTwoPointGame}. Tkachuk showed in that paper
that these games are perfect-information dual; Clontz and Holshouser previously showed these were Markov-information
dual in the case that \(X=C_p(Y)\) [TODO cite].

@@

\bibliographystyle{plain}
\bibliography{../../bibliography}

>>>>

The duality of the Rothberger game \(\schStrongSelGame{\mc O_X}{\mc O_X}\)
and the point-open game on \(X\) for perfect information strategies
was first noted by Galvin in \cite{MR0493925}, and
for Markov-information strategies by Clontz and Holshouser in
\cite{2018arXiv180606001C}. These proofs may be generalized as follows.

@@

In the case that \(\mc B=\mc O_X\), \(\schStrongSelGame{\mc O_X}{\mc O_X}\) is the well-known Rothberger game,
and \(\schStrongSelGame{\mc P_X}{\neg\mc O_X}\) is isomorphic
to the point-open game \(PO(X)\): \(\plI\) chooses points of \(X\), \(\plII\) chooses an open neighborhood
of each chosen point, and \(\plI\) wins if \(\plII\)'s choices are a cover.
So this was simply the classic result that the Rothberger game and
point-open game are perfect-information dual \cite{MR0493925}, and the more recent result that
these games are Markov-information dual \cite{2018arXiv180606001C}.

@@

Note that in the case that \(\mc B=\Omega_X\), \(\schStrongSelGame{\Omega_X}{\Omega_X}\) is the Rothberger
game played with \(\omega\)-covers, and \(\schStrongSelGame{\mc F_X}{\neg\Omega_X}\) is isomorphic
to the \(\Omega\)-finite-open game \(\Omega FO(X)\): \(\plI\) chooses finite subsets of \(X\), \(\plII\) chooses an open neighborhood
of each chosen finite set, and \(\plI\) wins if \(\plII\)'s choices are an \(\omega\)-cover.
These games were shown to be dual in \cite{2018arXiv180606001C}.

@@

In the case that \(\mc B=\Omega_{X,x}\) for some \(x\in X\), \(\schStrongSelGame{\mc D_X}{\Omega_{X,x}}\) is
the strong countable dense fan-tightness game at \(x\), see e.g. \cite{MR2678950}. \(\schStrongSelGame{\mc T_X}{\neg\Omega_{X,x}}\)
is the game \(CL(X,x)\) first studied by Tkachuk in \cite{tkachukTwoPointGame}. Tkachuk showed in that paper
that these games are perfect-information dual; Clontz and Holshouser previously showed these were Markov-information
dual in the case that \(X=C_p(Y)\)  \cite{2018arXiv180606001C}.

@@

\bibliographystyle{plain}
\bibliography{bibliography}
